Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-06 popl24/composition.tex
checkpoint

On the basis of the preceding we can prove our main result as
follows. Note that we assume a normal form of programs where the last
instruction is a decoding and public reveal of the output.
\begin{theorem}
  \label{theorem-gmw-NIMO}
  If $\eassign{\outv}{\ttt{decode}(e)}$ is a well-typed GMW circuit
  definition using certified components and
  $\config{\varnothing}{\eassign{\outv}{\ttt{decode}(e)}} \redxs
  \config{\prog}{\varnothing}$, then $\NIMO(\prog)$.
\end{theorem}
\begin{proof}
  Let $\iov(\prog) = S \cup (V \cup \outv)$. By definition of $\ttt{decode}$
  and assumptions of well-typedness we have for some $\ttt{g}$:
  $$
  \config{\varnothing}{\eassign{\outv}{\ttt{decode}(e)}} \redxs
  \config{\prog;\eassign{\outv}{\ttt{v[1,gout] xor v[2,gout]}}}{\varnothing}
  $$
  where by Lemmas \ref{lemma-gmw-encode} and \ref{lemma-gmw-preservation} we
  have $\sep{\progd(\prog)}{S_{\{1\}}}{V_{\{2\}}}$ and
  $\sep{\progd(\prog)}{S_{\{2\}}}{V_{\{1\}}}$. Since by properties of \ttt{xor} we have:
  $$
  \sep{\progd(\prog;\eassign{\outv}{\ttt{v[1,gout] xor v[2,gout]}})}{\{\outv\}}{\{\ttt{v[1,gout]}\}}
  $$
  and:
  $$
  \sep{\progd(\prog;\eassign{\outv}{\ttt{v[1,gout] xor v[2,gout]}})}{\{\outv\}}{\{\ttt{v2,gout]\}}
  $$
  therefore by Lemma \ref{lemma-gmw-frame}}:    
  $$
  \sep{\progd(\prog;\eassign{\outv}{\ttt{v[1,gout] xor v[2,gout]}})}{(S_{\{1\}} \cup \{ \outv \})}{V_{\{2\}}}
  $$
  and:
  $$
  \sep{\progd(\prog;\eassign{\outv}{\ttt{v[1,gout] xor v[2,gout]}})}{(S_{\{2\}} \cup \{ \outv \})}{V_{\{1\}}}
  $$
  The result follows.
\end{proof}

>>>>

On the basis of the preceding we can prove our main result as
follows. Note that we assume a normal form of programs where the last
instruction is a decoding and public reveal of the output.
\begin{theorem}
  \label{theorem-gmw-NIMO}
  If $\eassign{\outv}{\ttt{decode}(e)}$ is a well-typed GMW circuit
  definition using certified components and
  $\config{\varnothing}{\eassign{\outv}{\ttt{decode}(e)}} \redxs
  \config{\prog}{\varnothing}$, then $\NIMO(\prog)$.
\end{theorem}
\begin{proof}
  Let $\iov(\prog) = S \cup (V \cup \outv)$. By definition of $\ttt{decode}$
  and assumptions of well-typedness we have for some $\ttt{g}$:
  $$
  \config{\varnothing}{\eassign{\outv}{\ttt{decode}(e)}} \redxs
  \config{\prog;\eassign{\outv}{\ttt{v[1,gout] xor v[2,gout]}}}{\varnothing}
  $$
  where by Lemmas \ref{lemma-gmw-encode} and \ref{lemma-gmw-preservation} we
  have $\sep{\progd(\prog)}{S_{\{1\}}}{V_{\{2\}}}$ and
  $\sep{\progd(\prog)}{S_{\{2\}}}{V_{\{1\}}}$. This implies:
  $$\sep{\progd(\prog;\eassign{\outv}{\ttt{v[1,gout] xor v[2,gout]}})}{S_{\{1\}}}{V_{\{2\}}}$$ and:
  $$\sep{\progd(\prog;\eassign{\outv}{\ttt{v[1,gout] xor v[2,gout]}})}{S_{\{2\}}}{V_{\{1\}}}$$
  Thus:
  $\condd{\progd(\prog;\eassign{\outv}{\ttt{v[1,gout] xor v[2,gout]}})}{S_{\{1\}}}{V_{\{2\}} \cup \{ \outv \}}
  = \condd{\progd(\prog;\eassign{\outv}{\ttt{v[1,gout] xor v[2,gout]}})}{S_{\{1\}}}{\{ \outv \}}$
  and:
  $\condd{\progd(\prog;\eassign{\outv}{\ttt{v[1,gout] xor v[2,gout]}})}{S_{\{2\}}}{V_{\{1\}} \cup \{ \outv \}}
  = \condd{\progd(\prog;\eassign{\outv}{\ttt{v[1,gout] xor v[2,gout]}})}{S_{\{2\}}}{\{ \outv \}}$
\end{proof}
